---
title: "HW2"
author: "Roy Zhang"
date: "2022-10-06"
output: pdf_document
---

```{r}
library(tidyverse)
library(tidymodels)
library(magrittr)
library(yardstick)
abalone = read_csv("abalone.csv")
```

Question 1.
```{r}
abalone %<>% mutate(age = abalone$rings + 1.5)
hist(abalone$age, main = "Age Distribution", xlab = "Age")
```
The distribution of the data is skewed to the right. The range of the data is between 0 and 30. Most of the data points are between 8 and 14. 

Question 2.
```{r}
set.seed(1)
split = initial_split(abalone, strata = age)
training_set = training(split)
testing_set = testing(split)
```
Question 3.
```{r}
abalone_recipe <- recipe(age ~ ., data = select(training_set, -rings)) %>%
  step_dummy(all_nominal_predictors()) %>% 
  step_interact(terms = ~starts_with("type"):shucked_weight) %>%
  step_interact(terms = ~longest_shell:diameter) %>%
  step_interact(terms = ~shucked_weight:shell_weight) %>%
  step_normalize(all_predictors())
```
Question 4.
```{r}
lr_object = set_engine(linear_reg(), "lm")
```
Question 5.
```{r}
abalone_workflow = workflow() %>%
  add_model(lr_object) %>%
  add_recipe(abalone_recipe)
```
Question 6.
```{r}
abalone_fit = fit(abalone_workflow, training_set)
hypothetical_prediction = abalone_fit %>%
  predict(tibble(type = "F", longest_shell = 0.50, diameter = 0.10, 
                 height = 0.30, whole_weight = 4, shucked_weight = 1,
                 viscera_weight = 2, shell_weight = 1))
```
The predicted age of the hypothetical abalone is `r hypothetical_prediction$.pred`.

Question 7.
```{r}
assessment_set = metric_set(rsq, rmse, mae)
training_prediction = predict(abalone_fit, training_set)
predicted_vs_actual = bind_cols(predicted = training_prediction$.pred,
                                actual = training_set$age)
assessment_outcome = assessment_set(predicted_vs_actual, truth = actual,
                                    estimate = predicted)
```
The R-squared value is `r assessment_outcome$.estimate[1]`, the RMSE is `r assessment_outcome$.estimate[2]`, and the MAE is `r assessment_outcome$.estimate[3]`.

According to the R-squared value, `r assessment_outcome$.estimate[1]*100`% of the variability of the abalone's age can be explained by this regression. model.